---
title: "Data Definition Report"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
params:
  cores: 1
  analysis_folder: NULL
  bids_dir: NULL
  blood_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = FALSE)
# Warnings go to the console/step log, not into this report: dplyr's
# many-to-many join warning is the signal that a duplicated record has
# multiplied TAC rows, and it used to be discarded outright.
petfit::divert_report_warnings()

library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(knitr)
library(jsonlite)
library(plotly)
library(crosstalk)
library(htmltools)

# Fixed seed. The model fits use multstart, which draws its starting parameter
# sets at random; furrr_options(seed = TRUE) makes those draws parallel-safe but
# not reproducible, because it derives its streams from whatever state the
# session happens to be in. Seeding here makes a re-run of the same analysis
# give the same numbers, whatever `cores` is set to. Vary it deliberately if you
# want to know how seed-dependent a fit is.
set.seed(123)

theme_set(theme_light())

# Use parameters (from params or debugging section above)
analysis_folder <- params$analysis_folder
bids_dir <- params$bids_dir
blood_dir <- params$blood_dir

# Load configuration from standard location
config_path <- file.path(analysis_folder, "desc-petfitoptions_config.json")
config <- NULL
if (file.exists(config_path)) {
  tryCatch({
    config <- jsonlite::fromJSON(config_path)
    config <- coerce_bounds_numeric(config)
    cat("Loaded config from:", config_path, "\n")
  }, error = function(e) {
    cat("Warning: Could not load config file:", e$message, "\n")
  })
} else {
  cat("Config file not found at:", config_path, "\n")
}
```

This report summarises the data subsetting and individual TACs file creation step.

# Analysis Configuration

**Analysis folder:** `r params$analysis_folder`

**Generated on:** `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`

# Subsetting Parameters

The following subsetting criteria were applied to the combined TACs data:

## Dataset Subsetting

```{r dataset-subsetting-params}
if (!is.null(config$Subsetting)) {
  # Extract basic subsetting parameters (exclude tac_subset which is nested)
  basic_subsetting <- config$Subsetting
  basic_subsetting$tac_subset <- NULL  # Remove nested list

  subsetting_df <- tibble(
    Parameter = names(basic_subsetting),
    Value = map_chr(basic_subsetting, ~ if(.x == "" || is.null(.x)) "All" else as.character(.x))
  )
  kable(subsetting_df)
} else {
  cat("No subsetting parameters found in configuration file.")
}
```

## TAC Time Range Subsetting

```{r tac-subsetting-params}
#| results: asis

if (!is.null(config$Subsetting$tac_subset)) {
  tac_subset <- config$Subsetting$tac_subset

  # Format the subsetting information
  if (tac_subset$type == "frame") {
    str_glue("**Frame range:** {tac_subset$start} to {tac_subset$end}")
  } else if (tac_subset$type == "time") {
    str_glue("**Time range:** {tac_subset$start} to {tac_subset$end} minutes")
  }
} else {
  cat("**No TAC time range subsetting applied** - all frames included")
}
```

# Data Summary

```{r load-data}
# Read all generated TACs files for comprehensive statistics
tacs_files <- list.files(analysis_folder, 
                        pattern = "*_desc-combinedregions_tacs.tsv", 
                        recursive = TRUE)

tacdata <- tibble(
  filename = tacs_files
) %>% 
  mutate(basename = basename(filename)) %>% 
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>% 
  unnest(attributes) %>% 
  group_by(filename) %>% 
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>% 
  unnest(tacs) %>% 
  # pet column already exists in the individual files, so don't rename
  select(-measurement, -desc, -basename, -filename)
```

```{r tac-unit-conversion}
# Unit check: make sure that we're in kBq
tac_units_conversion <- standardise_analysis_tac_units(analysis_folder, tacs_files)
cat(tac_units_conversion$message, "\n")

if (tac_units_conversion$converted) {
  # The copy already loaded above, so that this report's own plots are in kBq
  # like everything downstream.
  tacdata <- tacdata %>%
    mutate(across(any_of(c("TAC", "seg_meanTAC")),
                  ~kinfitr::unit_convert(.x,
                                         from_units = tac_units_conversion$from_units,
                                         to_units = "kBq")))
}
```
 
Total measurements: `r length(unique(tacdata$pet))`

Total subjects: `r length(unique(tacdata$sub))`

Total regions: `r length(unique(tacdata$region))`

Total TACs: `r length(unique(  paste(tacdata$region, tacdata$pet) ))`

Total number of frames: `r nrow(tacdata)`

## Summary by PET Measurement

The following table lists the number of frames for each PET measurement in order to identify problematic measurements of measurements with missing time spans.

```{r measurement-summary}
pet_framesummary <- tacdata %>%
  ungroup() %>% 
  group_by(pet) %>% 
  filter(!duplicated(frame_start)) %>% 
  summarise(
    FramesCount = length(unique(frame_start)),
    StartTime = min(frame_start)/60,
    EndTime = max(frame_end)/60,
    DurationSum = sum(frame_dur)/60,
    MissingDuration = ((EndTime-StartTime)-DurationSum)/60,
    .groups = "drop"
  )

# Add min/max TAC values per PET measurement
tac_summary <- tacdata %>%
  ungroup() %>%
  group_by(pet) %>%
  summarise(
    MinTAC = round(min(TAC, na.rm = TRUE), 2),
    MaxTAC = round(max(TAC, na.rm = TRUE), 2),
    .groups = "drop"
  )

# Combine summaries
pet_framesummary <- pet_framesummary %>%
  left_join(tac_summary, by = "pet")

kable(pet_framesummary)
```


# Data Visualisation

```{r suv-outcome, echo=FALSE}
#| results: asis

if( sum(is.na(tacdata$InjectedRadioactivity)) == 0 &&
    sum(is.na(tacdata$bodyweight)) == 0 ) {
  
  suv_outcome <- "SUV"
  
  do_suv <- TRUE
  do_suv70 <- FALSE
  do_tac <- FALSE
  
  str_glue("SUV is calculated based on the InjectedRadioactivity dose and bodyweight because it is present for all measurements.")

  
}

if( sum(is.na(tacdata$InjectedRadioactivity)) == 0 &&
    sum(is.na(tacdata$bodyweight)) > 0 ) {
  
  suv_outcome <- "SUV_bw70"
  do_suv <- FALSE
  do_suv70 <- TRUE
  do_tac <- FALSE
  
  # An assumed body weight changes what the SUV axis means for every
  # measurement, so it is stated as a warning rather than a note.
  str_glue("> **Warning: SUV is approximated based on the InjectedRadioactivity ",
           "dose, but assuming a bodyweight of 70kg for all individuals because ",
           "this information is not available for all participants.** The assumed ",
           "weight is applied to every measurement, including those whose ",
           "bodyweight is known, so that SUV means the same thing across the ",
           "cohort. These SUVs are therefore approximate, and not comparable with ",
           "SUV calculated from measured bodyweights.")
  
}

if( sum(is.na(tacdata$InjectedRadioactivity)) > 0 ) {
  
  suv_outcome <- "TAC"
  do_suv <- FALSE
  do_suv70 <- FALSE
  do_tac <- TRUE
  
  str_glue("Plots are shown using TAC values and not SUV because the InjectedRadioactivity dose is not available for all measurements.")
  
}
```

```{r, eval=do_suv, echo=do_suv}
# Body weight in grams, not the kilograms it is recorded in: SUV is the tissue
# concentration over the dose per gram of body mass, which for a TAC in kBq/mL
# and a dose in kBq gives the conventional g/mL.
tacdata <- tacdata %>% 
  mutate(SUV = TAC / (InjectedRadioactivity/(bodyweight*1000)))

y_axis_title <- "SUV (g/mL)"
```

```{r, eval=do_suv70, echo=do_suv70}
tacdata <- tacdata %>% 
  mutate(SUV = TAC / (InjectedRadioactivity/(70*1000)))

y_axis_title <- "SUV (g/mL, assuming a bodyweight of 70kg)"
```

```{r, eval=do_tac, echo=do_tac}
tacdata <- tacdata %>% 
  mutate(SUV = TAC)

y_axis_title <- "TAC Radioactivity (kBq)"
```

## By Region

Here the TACs are shown for all PET measurements for each region.  Hover over individual TACs to see which measurement they belong to, and double click to reset the highlighting.


```{r tac-region-plots, fig.height=6, fig.width=8}
regplots <- tacdata %>% 
  mutate(tac = paste(pet, region)) %>% 
  group_by(region) %>% 
  nest() %>% 
  mutate(
    plot = map2(region, data, ~{
      shared_data <- SharedData$new(.y, ~tac)
      
      p <- ggplot(shared_data, aes(x = frame_mid/60, y = SUV, 
                                  group = tac, colour = tac,
                                  text = paste("PET:", pet))) +
        geom_point() +
        geom_line(linewidth = 0.5) +
        labs(title = .x,
             x = "Time (min)",
             y = y_axis_title) +
        guides(colour = "none") +
        theme_minimal()
      
      ggplotly(p, tooltip = "text", width = 800, height = 500) %>%
  highlight(on = "plotly_hover", off = "plotly_doubleclick", 
           opacityDim = 0.2) %>%
  layout(
    hovermode = "closest",
    updatemenus = list(
      list(
        type = "dropdown",
        x = 1,
        y = 1,
        buttons = list(
          list(
            method = "relayout",
            args = list(list(xaxis.type = "linear", yaxis.type = "linear")),
            label = "linear x / linear y"
          ),
          list(
            method = "relayout",
            args = list(list(xaxis.type = "log", yaxis.type = "linear")),
            label = "log x / linear y"
          ),
          list(
            method = "relayout",
            args = list(list(xaxis.type = "linear", yaxis.type = "log")),
            label = "linear x / log y"
          ),
          list(
            method = "relayout",
            args = list(list(xaxis.type = "log", yaxis.type = "log")),
            label = "log x / log y"
          )
        )
      )
    )
  )
    })
  ) %>% 
  pull(plot)

htmltools::tagList(map(regplots, ~htmltools::div(.x, style="width: 800px; height: 600px; margin-bottom: 20px;")))
```


## By PET

Here the TACs are shown for all regions for each PET measurement.  Hover over individual TACs to see which region they belong to, and double click to reset the highlighting.


```{r tac-pet-plots, fig.height=6, fig.width=8}
petplots <- tacdata %>% 
  mutate(tac = paste(pet, region)) %>% 
  group_by(pet) %>% 
  nest() %>% 
  mutate(
    plot = map2(pet, data, ~{
      shared_data <- SharedData$new(.y, ~tac)
      
      p <- ggplot(shared_data, aes(x = frame_mid/60, y = SUV, 
                                  group = tac, colour = tac,
                                  text = paste("Region:", region))) +
        geom_point() +
        geom_line(linewidth = 0.5) +
        labs(title = .x,
             x = "Time (min)",
             y = y_axis_title) +
        guides(colour = "none") +
        theme_minimal()
      
      ggplotly(p, tooltip = "text", width = 800, height = 500) %>%
  highlight(on = "plotly_hover", off = "plotly_doubleclick", 
           opacityDim = 0.2) %>%
  layout(
    hovermode = "closest",
    updatemenus = list(
      list(
        type = "dropdown",
        x = 1,
        y = 1,
        buttons = list(
          list(
            method = "relayout",
            args = list(list(xaxis.type = "linear", yaxis.type = "linear")),
            label = "linear x / linear y"
          ),
          list(
            method = "relayout",
            args = list(list(xaxis.type = "log", yaxis.type = "linear")),
            label = "log x / linear y"
          ),
          list(
            method = "relayout",
            args = list(list(xaxis.type = "linear", yaxis.type = "log")),
            label = "linear x / log y"
          ),
          list(
            method = "relayout",
            args = list(list(xaxis.type = "log", yaxis.type = "log")),
            label = "log x / log y"
          )
        )
      )
    )
  )
    })
  ) %>% 
  pull(plot)

htmltools::tagList(map(petplots, ~htmltools::div(.x, style="width: 800px; height: 600px; margin-bottom: 20px;")))
```


# Session Information

```{r session-info}
sessionInfo()
```
