---
title: "Nested 2TCM Model Fitting Report"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
params:
  cores: 1
  model_number: "Model 1"
  analysis_folder: NULL
  bids_dir: NULL
  blood_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = FALSE)
# Warnings go to the console/step log, not into this report: dplyr's
# many-to-many join warning is the signal that a duplicated record has
# multiplied TAC rows, and it used to be discarded outright.
petfit::divert_report_warnings()
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(kinfitr)
library(knitr)
library(jsonlite)
library(glue)
library(DT)
library(furrr)

# Fixed seed. The model fits use multstart, which draws its starting parameter
# sets at random; furrr_options(seed = TRUE) makes those draws parallel-safe but
# not reproducible, because it derives its streams from whatever state the
# session happens to be in. Seeding here makes a re-run of the same analysis
# give the same numbers, whatever `cores` is set to. Vary it deliberately if you
# want to know how seed-dependent a fit is.
set.seed(123)

theme_set(theme_light())

cores <- params$cores %||% 1
if (cores > 1) {
  if (future::supportsMulticore()) {
    future::plan(future::multicore, workers = cores)
  } else {
    future::plan(future::multisession, workers = cores)
  }
} else {
  future::plan(future::sequential)
}

# Use parameters (from params or debugging section above)
analysis_folder <- params$analysis_folder
# The units of the TACs everything downstream is derived from, recorded by
# the region definition step. Read rather than assumed, so that the sidecars
# written below cannot claim units the data does not have.
tac_units <- petfit_tac_units(analysis_folder)
model_number <- params$model_number
bids_dir <- params$bids_dir
blood_dir <- params$blood_dir

# Load configuration from standard location
config_path <- file.path(analysis_folder, "desc-petfitoptions_config.json")
config <- NULL
if (file.exists(config_path)) {
  tryCatch({
    config <- jsonlite::fromJSON(config_path)
    config <- coerce_bounds_numeric(config)
    # cat("Loaded config from:", config_path, "\n")
  }, error = function(e) {
    cat("Warning: Could not load config file:", e$message, "\n")
  })
} else {
  cat("Config file not found at:", config_path, "\n")
}
```

```{r, include=FALSE}
# Remove old files from previous runs
desc <- str_remove(str_to_lower(model_number), " ")

oldfiles <- list.files(analysis_folder, pattern=desc,
                       recursive = T, full.names = T)

file.remove(oldfiles)
```



This report summarises the nested 2TCM model fitting step. The nested 2TCM fits
all regions of each PET measurement jointly: the shared parameter(s) are
estimated across regions in an outer optimisation, while the remaining
parameters are fitted per region in an inner optimisation. The model uses the
macro parameterisation of the 2TCM, i.e. K1, Vnd, BPp and k4, from which k2,
k3, Vt and BPnd are derived.

# Analysis Configuration

**Model:** `r params$model_number` - Nested 2TCM (Two Tissue Compartment Model with shared parameters)

**Analysis folder:** `r params$analysis_folder`

**Generated on:** `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`

# Model Configuration and Parameters

```{r model-config}
# Extract model configuration for this specific model
model_config <- NULL
if (!is.null(config$Models)) {
  if (params$model_number == "Model 1") {
    model_config <- config$Models$Model1
  } else if (params$model_number == "Model 2") {
    model_config <- config$Models$Model2
  } else if (params$model_number == "Model 3") {
    model_config <- config$Models$Model3
  }
}

if (!is.null(model_config) && model_config$type == "nested2TCM") {

  shared <- model_config$shared %||% "Vnd"
  shared_display <- switch(shared,
                           "Vnd" = "Vnd",
                           "k4" = "k4",
                           "Vnd_k4" = "Vnd and k4",
                           shared)
  roiweights_setting <- model_config$roiweights %||% "volume"
  roiweights_display <- switch(roiweights_setting,
                               "volume" = "Volume-weighted",
                               "equal" = "Equal",
                               roiweights_setting)

  # Create configuration table
  config_items <- list(
    "Model Type" = "Nested 2TCM (Two Tissue Compartment Model with shared parameters)",
    "Shared Parameter(s)" = shared_display,
    "K1 Start Value" = model_config$K1$start %||% "Default",
    "K1 Lower Bound" = model_config$K1$lower %||% "Default",
    "K1 Upper Bound" = model_config$K1$upper %||% "Default",
    "Vnd Start Value" = model_config$Vnd$start %||% "Default",
    "Vnd Lower Bound" = model_config$Vnd$lower %||% "Default",
    "Vnd Upper Bound" = model_config$Vnd$upper %||% "Default",
    "BPp Start Value" = model_config$BPp$start %||% "Default",
    "BPp Lower Bound" = model_config$BPp$lower %||% "Default",
    "BPp Upper Bound" = model_config$BPp$upper %||% "Default",
    "k4 Start Value" = model_config$k4$start %||% "Default",
    "k4 Lower Bound" = model_config$k4$lower %||% "Default",
    "k4 Upper Bound" = model_config$k4$upper %||% "Default",
    "vB Value (fixed)" = model_config$vB_value %||% 0.05,
    "Region Weighting" = roiweights_display
  )

  # vB is always fixed in the nested 2TCM. The "vB Parameter Source" entry is
  # kept for consistency with the other model reports, which reference it in
  # their output sidecars.
  config_items[["Fit vB Parameter"]] <- "No"
  config_items[["vB Parameter Source"]] <- "Set to fixed value"

  # Add common parameters
  config_items[["Multstart Iterations"]] <- model_config$multstart_iter %||% 1

  # Add subset information if configured
  if (!is.null(model_config$subset)) {
    subset_info <- paste0(
      "Type: ", model_config$subset$type %||% "time",
      ", Start: ", model_config$subset$start %||% "Not set",
      ", End: ", model_config$subset$end %||% "Not set"
    )
    config_items[["TAC Subset"]] <- subset_info
  } else {
    config_items[["TAC Subset"]] <- "Use all frames"
  }

  config_df <- tibble(
    Parameter = names(config_items),
    Value = map_chr(config_items, as.character)
  )

  kable(config_df, caption = "Nested 2TCM Model Configuration")

} else {
  cat("Nested 2TCM model configuration not found or incomplete.")
}
```

```{r setup-conditions, echo=FALSE}
# Verify we have a valid nested 2TCM configuration
has_nested2tcm_config <- !is.null(model_config) && model_config$type == "nested2TCM"

# Exit early if not a nested 2TCM configuration
if (!has_nested2tcm_config) {
  cat("Invalid or missing nested 2TCM configuration. This report should not have been generated.")
  knitr::knit_exit()
}
```

# Loading Data

## Loading TAC Data

```{r load-tacs}
weights_files <- list.files(analysis_folder,
                        pattern = "*_weights.tsv",
                        recursive = TRUE)

weightsdata <- tibble(
  filename = weights_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>%
  unnest(tacs) %>%
  select(-filename, -basename, -measurement, -desc, -TAC)


tacs_files <- list.files(analysis_folder,
                        pattern = "*_desc-combinedregions_tacs.tsv",
                        recursive = TRUE)

tac_data <- tibble(
  filename = tacs_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>%
  unnest(tacs) %>%
  select(-basename, -measurement, -desc) %>%
  inner_join(weightsdata)
```

Because we are now working with kinetic modelling, we need to use minutes instead of seconds. Hence, we will henceforth use minutes for time.

```{r}
tac_data <- tac_data %>%
  mutate(frame_start = frame_start/60,
         frame_end = frame_end/60,
         frame_dur = frame_dur/60,
         frame_mid = frame_mid/60)
```


## Loading Blood Data

```{r blood-loading-setup, echo=FALSE}
# Determine which blood loading approach to use
if (!is.null(blood_dir)) {
  use_blood_dir <- TRUE
  use_analysis_folder <- FALSE
  use_bids_raw <- FALSE
} else {
  use_blood_dir <- FALSE
  blood_source <- determine_blood_source(analysis_folder, bids_dir)
  use_analysis_folder <- blood_source == "analysis_folder"
  use_bids_raw <- blood_source == "bids_dir"
}
```

```{r load-from-blood-dir, eval=use_blood_dir, echo=use_blood_dir}
# Load blood data from specified blood_dir
inputfunction_files <- list.files(blood_dir, pattern = "*_inputfunction\\.tsv$", recursive = TRUE, full.names = TRUE)

if (length(inputfunction_files) == 0) {
  stop("No inputfunction.tsv files found in blood_dir: ", blood_dir)
}

blood_data <- kinfitr::bloodstream_import_inputfunctions(blood_dir) %>%
  select(-measurement)
```

```{r load-from-analysis-folder, eval=use_analysis_folder, echo=use_analysis_folder}
# Load processed inputfunction files from analysis folder
inputfunction_files <- list.files(analysis_folder, pattern = "*_inputfunction\\.tsv$", recursive = TRUE, full.names = TRUE)

if (length(inputfunction_files) == 0) {
  stop("No inputfunction.tsv files found in analysis_folder: ", analysis_folder)
}

blood_data <- kinfitr::bloodstream_import_inputfunctions(analysis_folder) %>%
  select(-measurement, -desc)
```

```{r create-analysis-inputfunctions, eval=use_bids_raw, echo=use_bids_raw, results='asis'}
str_glue("Because we are loading blood data from the raw BIDS folder, we will first generate
         an arterial input function using linear interpolation of the measured curves,
         and then create *_inputfunction.tsv files in the petfit analysis folder.")
```

```{r load-from-bids-raw, eval=use_bids_raw}
# Load blood files from bids_dir
blood_files <- list.files(bids_dir, pattern = "*_blood\\.tsv$", recursive = TRUE, full.names = TRUE)

if (length(blood_files) == 0) {
  stop("No _blood.tsv files found in bids_dir")
}

# One input function per measurement, by linear interpolation of the measured
# curves. A measurement whose runs were merged in the region definition step
# carries no run entity, so it matches every run of its acquisition and their
# blood data is pooled into a single curve here.
inputfunction_result <- create_analysis_inputfunctions(bids_dir, tac_data, analysis_folder)
cat(paste0(inputfunction_result$messages, collapse = "\n"), "\n")

# Load the created inputfunction files
blood_data <- kinfitr::bloodstream_import_inputfunctions(analysis_folder) %>%
  select(-measurement, -desc)
```

```{r blood-loading-error, eval=(!use_blood_dir && !use_analysis_folder && !use_bids_raw)}
stop("No blood data available - provide blood_dir or ensure blood data exists in analysis folder or BIDS directory")
```

```{r check-blood-runs, echo=FALSE}
# The TACs and the input functions have to agree about runs. Where they do not,
# the join below would pair a measurement spanning both runs with the blood
# curve of only one of them, without saying so.
check_blood_run_alignment(tac_data, blood_data)
```

## Loading Delay Information

```{r load-delay}
delay_data <- tibble(
  filename = list.files(analysis_folder, pattern = "*_desc-delayfit_kinpar.tsv",
                       recursive = TRUE, full.names = TRUE)
)

if( nrow(delay_data)==0 ) {
  cat("No delay data found for kinetic modelling.")
  cat("Delay will be set to 0.")

  delay_source <- "Not estimated: assumed to be zero"

  delay_data <- blood_data %>%
    select(-input) %>%
    mutate(inpshift = 0)

} else{

  delay_data <- delay_data %>%
    # These are full paths, so the attributes are read from the basename: a
    # directory above the analysis folder can hold key-value pairs of its own
    # (a "rec-test" folder, say) which would otherwise be read as entities.
    mutate(attributes = map(filename, ~kinfitr::bids_filename_attributes(basename(.x)))) %>%
    unnest(attributes) %>%
    filter(!is.na(sub)) %>%
    mutate(pet = str_remove(basename(filename), "_model.*.*")) %>%
    mutate(pet = str_remove(basename(pet), "_desc.*")) %>%
    mutate(pet = str_remove(pet, "_kinpar.*")) %>%
    mutate(
      inpshift = map_dbl(filename, ~{
          tryCatch({
            delay <- read_tsv(.x)
            if (!is.null(delay$blood_timeshift)) {
              delay$blood_timeshift
            } else {
              0  # Default to zero if no delay found
            }
          }, error = function(e) 0)  # Default to zero on error
        })
      ) %>%
    select(-filename, -measurement, -model, -desc)

  delay_source <- "Inherited from delay fit"
}
```


# Combining Data

For the nested model, all regions of each PET measurement are fitted together,
so the data are nested by measurement (keeping `region` inside the nested TAC
data) rather than by measurement and region.

```{r}
tac_data_nested <- tac_data %>%
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet", "filename")))) %>%
  nest(.key="tacs")

model_data <- inner_join(tac_data_nested, blood_data,
                         # One blood record per measurement. A duplicate would
                         # otherwise multiply every region's TAC rows silently.
                         relationship = "many-to-one") %>%
  ungroup() %>%
  mutate(output_stem = filename) %>%
  select(-filename) %>%
  mutate(output_stem = str_remove(output_stem, "_desc.*")) %>%
  mutate(output_stem = str_remove(output_stem, "_weights.*")) %>%
  mutate(output_stem = str_remove(output_stem, "_tacs.*"))

model_data <- model_data %>%
  left_join(delay_data, relationship = "many-to-one")
```

## Checking Regions per Measurement

A nested model shares parameters across the regions of each measurement, so a
measurement with fewer than two regions cannot be fitted, and is excluded with
a warning.

```{r region-check, report_warnings=TRUE}
region_counts <- validate_min_regions_per_pet(tac_data, min_regions = 2)

sufficient_pets <- region_counts$pet[region_counts$sufficient]
model_data <- model_data %>%
  filter(pet %in% sufficient_pets)

region_counts %>%
  rename(`Number of Regions` = n_regions,
         `Sufficient for Nested Fitting` = sufficient) %>%
  kable(caption = "Regions per PET measurement")
```


# Nested 2TCM Model Fitting

Now we proceed to the actual nested 2TCM model fitting: one joint fit per PET
measurement, with `r shared_display` shared across regions.

```{r model-prep, report_warnings=TRUE}
# Extract model parameters from configuration
K1_start <- model_config$K1$start %||% 0.1
K1_lower <- model_config$K1$lower %||% 0.0001
K1_upper <- model_config$K1$upper %||% 1

Vnd_start <- model_config$Vnd$start %||% 1
Vnd_lower <- model_config$Vnd$lower %||% 0.0001
Vnd_upper <- model_config$Vnd$upper %||% 10

BPp_start <- model_config$BPp$start %||% 1
BPp_lower <- model_config$BPp$lower %||% 0.0001
BPp_upper <- model_config$BPp$upper %||% 50

k4_start <- model_config$k4$start %||% 0.1
k4_lower <- model_config$k4$lower %||% 0.0001
k4_upper <- model_config$k4$upper %||% 0.5

vB_value <- model_config$vB_value %||% 0.05

multstart_iter <- model_config$multstart_iter %||% 1

# Region weighting: larger regions provide more precise mean TACs, so their
# volumes are a sensible relative weighting for the shared parameter estimates
use_volume_roiweights <- roiweights_setting == "volume"
if (use_volume_roiweights && !"volume_mm3" %in% colnames(tac_data)) {
  warning("Volume-weighted region weighting was requested, but the combined ",
          "TACs carry no volume_mm3 column. Using equal region weights instead.")
  use_volume_roiweights <- FALSE
}

# Extract TAC subset parameters
subset_config <- model_config$subset
frameStartEnd <- NULL
timeStartEnd <- NULL

if (!is.null(subset_config) && (!is.null(subset_config$start) || !is.null(subset_config$end))) {
  if (subset_config$type == "frame") {
    frameStartEnd <- c(subset_config$start, subset_config$end)
  } else if (subset_config$type == "time") {
    timeStartEnd <- c(subset_config$start, subset_config$end)
  }
}
```


```{r model-fitting, report_warnings=TRUE}
# Safe nested 2TCM function to handle errors
safe_nested_2tcm <- possibly(nested_2tcm, otherwise = NA)

# Fit the nested 2TCM model, one joint fit per measurement
model_data <- model_data %>%
  mutate(fit_nested2tcm = future_pmap(list(tacs, input, inpshift),
                         ~safe_nested_2tcm(t_tac = ..1$frame_mid, tac = ..1$TAC,
                                 region = ..1$region,
                                 input = ..2,
                                 shared = shared,
                                 inpshift = ..3,
                                 vB = vB_value,
                                 weights = ..1$weights,
                                 roiweights = if (use_volume_roiweights) {
                                   ..1$volume_mm3
                                 } else {
                                   NULL
                                 },
                                 frameStartEnd = frameStartEnd,
                                 timeStartEnd = timeStartEnd,
                                 K1.start = K1_start,
                                 K1.lower = K1_lower,
                                 K1.upper = K1_upper,
                                 Vnd.start = Vnd_start,
                                 Vnd.lower = Vnd_lower,
                                 Vnd.upper = Vnd_upper,
                                 BPp.start = BPp_start,
                                 BPp.lower = BPp_lower,
                                 BPp.upper = BPp_upper,
                                 k4.start = k4_start,
                                 k4.lower = k4_lower,
                                 k4.upper = k4_upper,
                                 multstart_iter = multstart_iter),
                         .options = furrr_options(seed = TRUE))) %>%
  ungroup() %>%
  mutate(success = map_dbl(fit_nested2tcm, length) > 1)
```

```{r, results='asis'}
success_n <- sum(model_data$success)
tot_n <- nrow(model_data)

str_glue("Model successfully estimated for {success_n} / {tot_n} ({round(100*success_n/tot_n)}%) of measurements.

         Model estimation unsuccessful for {tot_n-success_n} / {tot_n}  ({100-(round(100*success_n/tot_n))}%) of measurements.")
```

# Results

```{r}
model_data <- model_data %>%
  filter(success)
```


## Shared Parameters

The shared parameter(s) (`r shared_display`) take a single value per PET
measurement. Standard errors, where shown, are expressed as a fraction of the
estimate, and are approximate: they are derived from the curvature of the
profiled objective at the optimum.

```{r}
shared_par_table <- model_data %>%
  mutate(shared_pars = map(fit_nested2tcm, ~{
    outer_names <- .x$outer_pars
    est <- .x$par %>%
      slice(1) %>%
      select(all_of(outer_names))
    ses <- .x$par.se %>%
      slice(1) %>%
      select(any_of(paste0(outer_names, ".se")))
    bind_cols(est, ses)
  })) %>%
  select(-fit_nested2tcm, -tacs, -input) %>%
  select(-output_stem) %>%
  select(-any_of(c("vB", "inpshift"))) %>%
  unnest(shared_pars) %>%
  select(where(~ mean(is.na(.x)) < 1))

shared_par_table %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

### Shared Parameter Histograms

```{r, fig.width=7, fig.height=4}
shared_par_long <- shared_par_table %>%
  pivot_longer(cols = any_of(c("Vnd", "k4")),
               names_to = "Parameter",
               values_to = "Value")

ggplot(shared_par_long, aes(x=Value, fill=Parameter)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free", ncol=2) +
  guides(fill="none")
```


## Parameters

```{r}
model_res <- model_data %>%
  ungroup() %>%
  mutate(par = map(fit_nested2tcm, "par")) %>%
  select(-fit_nested2tcm, -tacs, -input)
```

### Estimates

```{r}
par_table <- model_res %>%
  select(-output_stem) %>%
  select(-any_of(c("vB", "inpshift"))) %>%
  unnest(par)

par_table %>%
  select(where(~ n_distinct(.x) > 1)) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

### Standard Error

Here is shown the standard error as a fraction of the mean value (i.e. 1 = 100\%).
Standard errors of the shared parameters are approximate (see above), and
repeated for each region of the measurement they belong to.

```{r}
par_se_table <- model_data %>%
  ungroup() %>%
  mutate(par.se = map(fit_nested2tcm, "par.se")) %>%
  select(-fit_nested2tcm, -tacs, -input) %>%
  select(-output_stem) %>%
  select(-any_of(c("vB", "inpshift"))) %>%
  unnest(par.se) %>%
  select(where(~ mean(is.na(.x)) < 1))

par_se_table %>%
  select(where(~ n_distinct(.x) > 1)) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

### Goodness of Fit

The nested fit optimises a joint objective across regions, so the per-region
AIC and BIC of the independent models are not defined here: the effective
number of parameters per region is ambiguous when parameters are shared. The
weighted residual sum of squares is reported per region, along with the joint
objective value (the region-weighted sum of the weighted residual sums of
squares) and the optimiser convergence code (0 = converged) per measurement.

```{r}
gof_table <- model_data %>%
  ungroup() %>%
  mutate(gof = map(fit_nested2tcm, ~ .x$tacs %>%
    group_by(region = Region) %>%
    summarise(RSS = sum(Weights * (Radioactivity - Fitted)^2, na.rm = TRUE),
              n_frames = n(),
              .groups = "drop"))) %>%
  select(-fit_nested2tcm, -tacs, -input) %>%
  select(-output_stem) %>%
  select(-any_of(c("vB", "inpshift"))) %>%
  unnest(gof) %>%
  select(where(~ mean(is.na(.x)) < 1))

gof_table %>%
  select(where(~ n_distinct(.x) > 1)) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

```{r}
exam_gof_table <- model_data %>%
  ungroup() %>%
  mutate(objective = map_dbl(fit_nested2tcm, ~ .x$fit$value),
         convergence = map_dbl(fit_nested2tcm, ~ .x$fit$convergence)) %>%
  select(-fit_nested2tcm, -tacs, -input) %>%
  select(-output_stem) %>%
  select(-any_of(c("vB", "inpshift")))

exam_gof_table %>%
  select(where(~ n_distinct(.x) > 1), objective, convergence) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable(caption = "Measurement-level joint objective and convergence")
```

### Parameter Plots

#### Overall Histogram

```{r, fig.width=7, fig.height=9}
par_table_long <- par_table %>%
  pivot_longer(cols=c(K1, k2, k3, k4, Vt, Vnd, BPp, BPnd),
               names_to = "Parameter",
               values_to = "Value")


ggplot(par_table_long, aes(x=Value, fill=Parameter)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free", ncol=2) +
  guides(fill="none")
```


#### Histograms By Region

```{r, fig.width=7, fig.height=9}
ggplot(par_table_long, aes(x=Value, fill=region)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free", ncol=2)
```


## Fits

### Plots

Each measurement produces one joint fit across its regions; the fit plots are
faceted by region, with up to three regions per page.

```{r, results='asis'}
n_fit_meas <- nrow(model_data %>% filter(success))
embed_fit_plots <- n_fit_meas <= 50

if (embed_fit_plots) {
  fit_plot_dir <- tempdir()
} else {
  fit_plot_dir <- file.path(analysis_folder, "reports",
                        paste0(desc, "_report_plots"), "fit")
  dir.create(fit_plot_dir, recursive = TRUE, showWarnings = FALSE)
}

fit_plot_files <- model_data %>%
  filter(success) %>%
  mutate(safe_filename = str_replace_all(pet, "[^A-Za-z0-9_-]", "_")) %>%
  {future_pmap(
    list(.$fit_nested2tcm, .$pet, .$safe_filename),
    function(fit, pet, fname) {
      pages <- plot(fit)
      if (inherits(pages, "ggplot")) pages <- list(pages)
      imap_chr(pages, function(p, i) {
        p <- p +
          labs(subtitle = pet, y = "Radioactivity (kBq)", x = "Time (min)") +
          theme_light()
        filepath <- file.path(fit_plot_dir,
                              paste0("fit_", fname, "_page", i, ".png"))
        ggsave(filepath, p, width = 9, height = 4, dpi = 96)
        filepath
      })
    }, .options = furrr_options(seed = TRUE))} %>%
  flatten_chr()

if (embed_fit_plots) {
  walk(fit_plot_files, ~cat("![](", .x, ")\n\n", sep = ""))
} else {
  cat(str_glue("\n\n**Note:** fit plots for {n_fit_meas} measurements saved to: `reports/{desc}_report_plots/fit/`\n\n"))
}
```

### Residuals

```{r, results='asis'}
n_res_meas <- nrow(model_data %>% filter(success))
embed_res_plots <- n_res_meas <= 50

if (embed_res_plots) {
  res_plot_dir <- tempdir()
} else {
  res_plot_dir <- file.path(analysis_folder, "reports",
                        paste0(desc, "_report_plots"), "residuals")
  dir.create(res_plot_dir, recursive = TRUE, showWarnings = FALSE)
}

res_plot_files <- model_data %>%
  filter(success) %>%
  mutate(safe_filename = str_replace_all(pet, "[^A-Za-z0-9_-]", "_")) %>%
  {future_pmap_chr(
    list(.$fit_nested2tcm, .$pet, .$safe_filename),
    function(fit, pet, fname) {
      resid_data <- fit$tacs %>%
        mutate(Residuals = Radioactivity - Fitted)
      p <- ggplot(resid_data, aes(x = Time, y = Residuals)) +
        geom_point(aes(size = Weights)) +
        geom_line(alpha = 0.5) +
        geom_hline(yintercept = 0, linetype = "dashed") +
        facet_wrap(~Region) +
        scale_size(range = c(1, 3)) +
        guides(size = "none") +
        labs(title = pet, x = "Time (min)", y = "Residuals") +
        theme_light()
      filepath <- file.path(res_plot_dir, paste0("res_", fname, ".png"))
      ggsave(filepath, p, width = 9, height = 6, dpi = 96)
      filepath
    }, .options = furrr_options(seed = TRUE))}

if (embed_res_plots) {
  walk(res_plot_files, ~cat("![](", .x, ")\n\n", sep = ""))
} else {
  cat(str_glue("\n\n**Note:** residual plots for {n_res_meas} measurements saved to: `reports/{desc}_report_plots/residuals/`\n\n"))
}
```




# Saving Parameters

## Main TSV

```{r}
savepar <- inner_join(par_table,
                      par_se_table) %>%
  inner_join(gof_table) %>%
  # Fixing parameter names
  rename_with(~str_replace(.x, "\\.se", "-se")) %>%
  rename_with(~str_replace(.x, "Vt", "VT"))

write_tsv(savepar,
          file=paste0(analysis_folder, "/",
                      "model-", "nested2TCM","_",
                      "desc-", desc,"_",
                      "kinpar.tsv"))
```

## PET Folder TSVs

```{r}
folder_data <- tibble(
  filename = tacs_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  mutate(dirname = dirname(filename)) %>%
  select(-filename, -basename, -measurement, -desc)

savepar_pet <- savepar %>%
    group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet")))) %>%
  nest(.key="kinpars") %>%
  inner_join(folder_data) %>%
  mutate(filename = paste0(analysis_folder, "/", dirname, "/", pet, "_",
                           "model-", "nested2TCM","_",
                            "desc-", desc,"_",
                            "kinpar.tsv"))

walk2(savepar_pet$kinpars, savepar_pet$filename, ~write_tsv(.x, .y))
```

```{r}
savepar_pet <- savepar_pet %>%
  group_by(pet) %>%
  mutate(jsondat = map(kinpars, ~c(list(
      Description = paste("Nested two tissue compartmental model (macro parameterisation)",
                          "fit using nonlinear least squares estimation, with parameters",
                          "shared across regions within each measurement."),
      ModelName = "nested2TCM",
      AdditionalModelDetails = str_glue("Shared parameter(s): {shared_display}. vB fixed at {vB_value}. Region weighting: {config_items$`Region Weighting`}. Blood delay source: {delay_source}")),
      kinpar_units(names(.x), tac_units$radioactivity)))) %>%
  mutate(jsondat = map_chr(jsondat, ~jsonlite::toJSON(.x, pretty = TRUE, auto_unbox = TRUE))) %>%
  mutate(filename_json = str_replace(filename, ".tsv", ".json"))

walk2(savepar_pet$jsondat,
      savepar_pet$filename_json,
      ~writeLines(.x, .y))
```

# Saving Fitted Values

## PET Folder TSVs

```{r}
savefits <- model_data %>%
  filter(success) %>%
  mutate(fitvals = map(fit_nested2tcm, ~{

    measured <- .x$tacs %>%
      transmute(region = Region,
                frame_mid = Time,
                TAC = Radioactivity,
                weights = Weights)

    interpfitvals <- crossing(
      region = unique(.x$tacs$Region),
      frame_mid = seq(from=min(.x$tacs$Time),
                      to=max(.x$tacs$Time),
                      length.out=500))

    # predict.nested_2tcm requires a data frame (it uses nrow()), with columns
    # t_tac and region
    interpfitvals$TAC_fitted <- predict(
      .x, newdata = tibble(t_tac = interpfitvals$frame_mid,
                           region = interpfitvals$region))

    measured %>%
      full_join(interpfitvals) %>%
      arrange(region, frame_mid)
  })) %>%
  # Entities are optional: a study whose files name no session has no ses
  # column. pet, inpshift and fitvals are required, so they stay strict and a
  # genuine absence still errors.
  select(any_of(c("sub", "ses", "task", "trc", "run", "rec")),
         pet, inpshift, fitvals) %>%
  unnest(cols=c("fitvals")) %>%
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet")))) %>%
  nest(.key="fitvals")

savefits_pet <- savefits %>%
  inner_join(folder_data) %>%
  mutate(filename = paste0(analysis_folder, "/", dirname, "/", pet, "_",
                           "model-", "nested2TCM","_",
                            "desc-", desc,"fitted",
                            "_",
                            "tacs.tsv"))

walk2(savefits_pet$fitvals, savefits_pet$filename, ~write_tsv(.x, .y))
```

```{r}
savefits_pet <- savefits_pet %>%
  group_by(pet) %>%
  mutate(jsondat = map(fitvals, ~c(list(
      Description = "Nested two tissue compartment model fitted values.",
      ModelName = "nested2TCM",
      AdditionalModelDetails = str_glue("Shared parameter(s): {shared_display}. vB fixed at {vB_value}. Region weighting: {config_items$`Region Weighting`}. Blood delay source: {delay_source}")),
      bids_column_units(list(
        frame_mid = "The frame middle time",
        TAC = paste("TAC radioactivity data to which the model was fitted.",
                  "If there is a vB, this is after removal of blood radioactivity."),
        TAC_fitted = "Model fitted values.",
        weights = "Model weights"),
        radioactivity_units = tac_units$radioactivity,
        time_units = "min")))) %>%
  mutate(jsondat = map_chr(jsondat, ~jsonlite::toJSON(.x, pretty = TRUE, auto_unbox = TRUE))) %>%
  mutate(filename_json = str_replace(filename, ".tsv", ".json"))

walk2(savefits_pet$jsondat,
      savefits_pet$filename_json,
      ~writeLines(.x, .y))
```




```{r cleanup, include=FALSE}
future::plan(future::sequential)
```

# Session Information

```{r session-info}
sessionInfo()
```
