---
title: "Nested SRTM Model Fitting Report"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
params:
  cores: 1
  model_number: "Model 1"
  analysis_folder: NULL
  bids_dir: NULL
  blood_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = FALSE)
# Warnings go to the console/step log, not into this report: dplyr's
# many-to-many join warning is the signal that a duplicated record has
# multiplied TAC rows, and it used to be discarded outright.
petfit::divert_report_warnings()
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(kinfitr)
library(knitr)
library(jsonlite)
library(glue)
library(DT)
library(furrr)

# Fixed seed. The model fits use multstart, which draws its starting parameter
# sets at random; furrr_options(seed = TRUE) makes those draws parallel-safe but
# not reproducible, because it derives its streams from whatever state the
# session happens to be in. Seeding here makes a re-run of the same analysis
# give the same numbers, whatever `cores` is set to. Vary it deliberately if you
# want to know how seed-dependent a fit is.
set.seed(123)

cores <- params$cores %||% 1
if (cores > 1) {
  if (future::supportsMulticore()) {
    future::plan(future::multicore, workers = cores)
  } else {
    future::plan(future::multisession, workers = cores)
  }
} else {
  future::plan(future::sequential)
}

theme_set(theme_light())

# Use parameters (from params or debugging section above)
analysis_folder <- params$analysis_folder
model_number <- params$model_number
bids_dir <- params$bids_dir

# Load configuration from standard location
config_path <- file.path(analysis_folder, "desc-petfitoptions_config.json")
config <- NULL
if (file.exists(config_path)) {
  tryCatch({
    config <- jsonlite::fromJSON(config_path)
    config <- coerce_bounds_numeric(config)
  }, error = function(e) {
    cat("Warning: Could not load config file:", e$message, "\n")
  })
} else {
  cat("Config file not found at:", config_path, "\n")
}
```

```{r, include=FALSE}
# Remove old files from previous runs
desc <- str_remove(str_to_lower(model_number), " ")

oldfiles <- list.files(analysis_folder, pattern=desc,
                       recursive = T, full.names = T)

file.remove(oldfiles)
```



This report summarises the model fitting step using the nested Simplified
Reference Tissue Model. The nested SRTM fits all regions of each PET
measurement jointly using the SRTM2 parameterisation (Wu & Carson, 2002):
a single shared k2' is estimated across regions in an outer optimisation,
while R1 and BPnd are fitted per region in an inner optimisation. Estimating
k2' by leveraging information across regions in this way is the principled way
to obtain the shared k2' value that SRTM2 requires.

> Lammertsma AA, Hume SP. Simplified reference tissue model for PET receptor studies. Neuroimage. 1996 Dec 31;4(3):153-8.

> Wu Y, Carson RE. Noise reduction in the simplified reference tissue model for neuroreceptor functional imaging. J Cereb Blood Flow Metab. 2002 Dec;22(12):1440-52.

The fitted k2' values are written into the kinetic parameter outputs, so later
models configured to inherit k2' from this model (SRTM2, refLogan, MRTM2 with
`inherit_model...` sources) pick them up automatically.

# Analysis Configuration

**Model:** `r params$model_number` - Nested SRTM (shared k2' within each measurement)

**Analysis folder:** `r params$analysis_folder`

**Generated on:** `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`

# Model Configuration and Parameters

```{r model-config}
# Extract model configuration for this specific model
model_config <- NULL
if (!is.null(config$Models)) {
  if (params$model_number == "Model 1") {
    model_config <- config$Models$Model1
  } else if (params$model_number == "Model 2") {
    model_config <- config$Models$Model2
  } else if (params$model_number == "Model 3") {
    model_config <- config$Models$Model3
  }
}

if (!is.null(model_config) && model_config$type == "nestedSRTM") {

  roiweights_setting <- model_config$roiweights %||% "volume"
  roiweights_display <- switch(roiweights_setting,
                               "volume" = "Volume-weighted",
                               "equal" = "Equal",
                               roiweights_setting)

  # Create configuration table
  config_items <- list(
    "Model Type" = "Nested SRTM (shared k2' within each measurement)",
    "R1 Start Value" = model_config$R1$start %||% "Default",
    "R1 Lower Bound" = model_config$R1$lower %||% "Default",
    "R1 Upper Bound" = model_config$R1$upper %||% "Default",
    "BPnd Start Value" = model_config$BPnd$start %||% "Default",
    "BPnd Lower Bound" = model_config$BPnd$lower %||% "Default",
    "BPnd Upper Bound" = model_config$BPnd$upper %||% "Default",
    "k2prime Start Value" = model_config$k2prime$start %||% "Default",
    "k2prime Lower Bound" = model_config$k2prime$lower %||% "Default",
    "k2prime Upper Bound" = model_config$k2prime$upper %||% "Default",
    "Region Weighting" = roiweights_display,
    "Multstart Iterations" = model_config$multstart_iter %||% 1
  )

  # Add subset information if configured
  if (!is.null(model_config$subset)) {
    subset_info <- paste0(
      "Type: ", model_config$subset$type %||% "time",
      ", Start: ", model_config$subset$start %||% "Not set",
      ", End: ", model_config$subset$end %||% "Not set"
    )
    config_items[["TAC Subset"]] <- subset_info
  } else {
    config_items[["TAC Subset"]] <- "Use all frames"
  }

  config_df <- tibble(
    Parameter = names(config_items),
    Value = map_chr(config_items, as.character)
  )

  kable(config_df, caption = "Nested SRTM Model Configuration")

} else {
  cat("Nested SRTM model configuration not found or incomplete.")
}
```

```{r setup-conditions, echo=FALSE}
# Verify we have a valid nested SRTM configuration
has_nestedsrtm_config <- !is.null(model_config) && model_config$type == "nestedSRTM"

# Exit early if not a nested SRTM configuration
if (!has_nestedsrtm_config) {
  cat("Invalid or missing nested SRTM configuration. This report should not have been generated.")
  knitr::knit_exit()
}
```

# Loading Data

## Loading TAC Data

```{r load-tacs}
weights_files <- list.files(analysis_folder,
                        pattern = "*_weights.tsv",
                        recursive = TRUE)

weightsdata <- tibble(
  filename = weights_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>%
  unnest(tacs) %>%
  select(-filename, -basename, -measurement, -desc, -TAC)


tacs_files <- list.files(analysis_folder,
                        pattern = "*_desc-targetregions_tacs.tsv",
                        recursive = TRUE)

tac_data <- tibble(
  filename = tacs_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>%
  unnest(tacs) %>%
  select(-basename, -measurement, -desc) %>%
  inner_join(weightsdata)
```




## Loading Reference TAC Data

```{r load-reftac}
ref_files <- list.files(analysis_folder,
                        pattern = "*_desc-ref_tacs.tsv",
                        recursive = TRUE)

if (length(ref_files) == 0) {
  stop("No reference TAC files found in analysis folder: ", analysis_folder)
}

ref_data <- tibble(
  filename = ref_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(ref_tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>%
  unnest(ref_tacs) %>%
  select(-basename, -measurement, -desc, -filename) %>%
  select(-volume_mm3)
```


# Combining Data

For the nested model, all regions of each PET measurement are fitted together,
so the data are nested by measurement (keeping `region` inside the nested TAC
data) rather than by measurement and region.

```{r}
model_data <- tac_data %>%
  inner_join(ref_data) %>%
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet", "filename")))) %>%
  mutate(frame_start = frame_start/60,
         frame_end = frame_end/60,
         frame_dur = frame_dur/60,
         frame_mid = frame_mid/60) %>%
  nest(.key="tacs") %>%
  ungroup() %>%
  mutate(output_stem = filename) %>%
  select(-filename) %>%
  mutate(output_stem = str_remove(output_stem, "_desc.*")) %>%
  mutate(output_stem = str_remove(output_stem, "_weights.*")) %>%
  mutate(output_stem = str_remove(output_stem, "_tacs.*"))
```

## Checking Regions per Measurement

A nested model shares k2' across the regions of each measurement, so a
measurement with fewer than two regions cannot be fitted, and is excluded with
a warning.

```{r region-check, report_warnings=TRUE}
region_counts <- validate_min_regions_per_pet(tac_data, min_regions = 2)

sufficient_pets <- region_counts$pet[region_counts$sufficient]
model_data <- model_data %>%
  filter(pet %in% sufficient_pets)

region_counts %>%
  rename(`Number of Regions` = n_regions,
         `Sufficient for Nested Fitting` = sufficient) %>%
  kable(caption = "Regions per PET measurement")
```


# Nested SRTM Model Fitting

Now we proceed to the actual nested SRTM model fitting: one joint fit per PET
measurement, with k2' shared across regions.

```{r model-prep, report_warnings=TRUE}
# Extract model parameters from configuration
R1_start <- model_config$R1$start %||% 1
R1_lower <- model_config$R1$lower %||% 0
R1_upper <- model_config$R1$upper %||% 10

bp_start <- model_config$BPnd$start %||% 1.5
bp_lower <- model_config$BPnd$lower %||% 0
bp_upper <- model_config$BPnd$upper %||% 15

k2prime_start <- model_config$k2prime$start %||% 0.1
k2prime_lower <- model_config$k2prime$lower %||% 0.001
k2prime_upper <- model_config$k2prime$upper %||% 1

multstart_iter <- model_config$multstart_iter %||% 1

# Region weighting: larger regions provide more precise mean TACs, so their
# volumes are a sensible relative weighting for the shared k2' estimate
use_volume_roiweights <- roiweights_setting == "volume"
if (use_volume_roiweights && !"volume_mm3" %in% colnames(tac_data)) {
  warning("Volume-weighted region weighting was requested, but the target ",
          "region TACs carry no volume_mm3 column. Using equal region weights ",
          "instead.")
  use_volume_roiweights <- FALSE
}

# Extract TAC subset parameters
subset_config <- model_config$subset
frameStartEnd <- NULL
timeStartEnd <- NULL

if (!is.null(subset_config) && (!is.null(subset_config$start) || !is.null(subset_config$end))) {
  if (subset_config$type == "frame") {
    frameStartEnd <- c(subset_config$start, subset_config$end)
  } else if (subset_config$type == "time") {
    timeStartEnd <- c(subset_config$start, subset_config$end)
  }
}
```


```{r model-fitting, report_warnings=TRUE}
# Safe nested SRTM function to handle errors
safe_nested_srtm <- possibly(nested_srtm, otherwise = NA)

# Fit the nested SRTM model, one joint fit per measurement
model_data <- model_data %>%
  mutate(fit_nestedsrtm = future_map(tacs,
                         ~safe_nested_srtm(t_tac = .x$frame_mid,
                                    roitac = .x$TAC,
                                    reftac = .x$RefTAC,
                                    region = .x$region,
                                    weights = .x$weights,
                                    roiweights = if (use_volume_roiweights) {
                                      .x$volume_mm3
                                    } else {
                                      NULL
                                    },
                                    frameStartEnd = frameStartEnd,
                                    timeStartEnd = timeStartEnd,
                                    R1.start = R1_start,
                                    R1.lower = R1_lower,
                                    R1.upper = R1_upper,
                                    bp.start = bp_start,
                                    bp.lower = bp_lower,
                                    bp.upper = bp_upper,
                                    k2prime.start = k2prime_start,
                                    k2prime.lower = k2prime_lower,
                                    k2prime.upper = k2prime_upper,
                                    multstart_iter = multstart_iter),
                         .options = furrr_options(seed = TRUE))) %>%
  mutate(success = map_dbl(fit_nestedsrtm, length) > 1)
```

```{r, results='asis'}
success_n <- sum(model_data$success)
tot_n <- nrow(model_data)

str_glue("Model successfully estimated for {success_n} / {tot_n} ({round(100*success_n/tot_n)}%) of measurements.

         Model estimation unsuccessful for {tot_n-success_n} / {tot_n}  ({100-(round(100*success_n/tot_n))}%) of measurements.")
```

# Results

```{r}
model_data <- model_data %>%
  filter(success)
```


## Shared k2'

The shared k2' takes a single value per PET measurement. Standard errors,
where shown, are expressed as a fraction of the estimate, and are approximate:
they are derived from the curvature of the profiled objective at the optimum.

```{r}
shared_par_table <- model_data %>%
  mutate(shared_pars = map(fit_nestedsrtm, ~{
    est <- .x$par %>%
      slice(1) %>%
      select(k2prime)
    ses <- .x$par.se %>%
      slice(1) %>%
      select(any_of("k2prime.se"))
    bind_cols(est, ses)
  })) %>%
  select(-fit_nestedsrtm, -tacs) %>%
  select(-output_stem) %>%
  unnest(shared_pars) %>%
  select(where(~ mean(is.na(.x)) < 1))

shared_par_table %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

### Shared k2' Histogram

```{r, fig.width=5, fig.height=4}
ggplot(shared_par_table, aes(x=k2prime)) +
  geom_histogram(fill="blue", colour="grey") +
  labs(title = "Distribution of Shared k2' Estimates",
       x = "k2' (shared within measurement)")
```


## Parameters

```{r}
model_res <- model_data %>%
  ungroup() %>%
  mutate(par = map(fit_nestedsrtm, "par")) %>%
  select(-fit_nestedsrtm, -tacs)
```

### Estimates

```{r}
par_table <- model_res %>%
  select(-output_stem) %>%
  unnest(par) %>%
  rename(BPnd = bp)

par_table %>%
  select(where(~ n_distinct(.x) > 1)) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

### Standard Error

Here is shown the standard error as a fraction of the mean value (i.e. 1 = 100\%).
The standard error of the shared k2' is approximate (see above), and repeated
for each region of the measurement it belongs to.

```{r}
par_se_table <- model_data %>%
  ungroup() %>%
  mutate(par.se = map(fit_nestedsrtm, "par.se")) %>%
  select(-fit_nestedsrtm, -tacs) %>%
  select(-output_stem) %>%
  unnest(par.se) %>%
  select(where(~ mean(is.na(.x)) < 1)) %>%
  rename(BPnd.se = bp.se)

par_se_table %>%
  select(where(~ n_distinct(.x) > 1)) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

### Goodness of Fit

The nested fit optimises a joint objective across regions, so the per-region
AIC and BIC of the independent models are not defined here: the effective
number of parameters per region is ambiguous when a parameter is shared. The
weighted residual sum of squares is reported per region, along with the joint
objective value (the region-weighted sum of the weighted residual sums of
squares) and the optimiser convergence code (0 = converged) per measurement.

```{r}
gof_table <- model_data %>%
  ungroup() %>%
  mutate(gof = map(fit_nestedsrtm, ~ .x$tacs %>%
    group_by(region = Region) %>%
    summarise(RSS = sum(Weights * (Radioactivity - Fitted)^2, na.rm = TRUE),
              n_frames = n(),
              .groups = "drop"))) %>%
  select(-fit_nestedsrtm, -tacs) %>%
  select(-output_stem) %>%
  unnest(gof) %>%
  select(where(~ mean(is.na(.x)) < 1))

gof_table %>%
  select(where(~ n_distinct(.x) > 1)) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable()
```

```{r}
exam_gof_table <- model_data %>%
  ungroup() %>%
  mutate(objective = map_dbl(fit_nestedsrtm, ~ .x$fit$value),
         convergence = map_dbl(fit_nestedsrtm, ~ .x$fit$convergence)) %>%
  select(-fit_nestedsrtm, -tacs) %>%
  select(-output_stem)

exam_gof_table %>%
  select(where(~ n_distinct(.x) > 1), objective, convergence) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  DT::datatable(caption = "Measurement-level joint objective and convergence")
```

### Parameter Plots

#### Overall Histogram

```{r, fig.width=7, fig.height=7}
par_table_long <- par_table %>%
  pivot_longer(cols=c(R1, BPnd, k2prime, k2a),
               names_to = "Parameter",
               values_to = "Value")


ggplot(par_table_long, aes(x=Value, fill=Parameter)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free", ncol=2) +
  guides(fill="none")
```


#### Histograms By Region

```{r, fig.width=7, fig.height=7}
ggplot(par_table_long, aes(x=Value, fill=region)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free", ncol=2)
```


## Fits

### Plots

Each measurement produces one joint fit across its regions; the fit plots are
faceted by region, with up to three regions per page.

```{r, results='asis'}
n_fit_meas <- nrow(model_data %>% filter(success))
embed_fit_plots <- n_fit_meas <= 50

if (embed_fit_plots) {
  fit_plot_dir <- tempdir()
} else {
  fit_plot_dir <- file.path(analysis_folder, "reports",
                        paste0(desc, "_report_plots"), "fit")
  dir.create(fit_plot_dir, recursive = TRUE, showWarnings = FALSE)
}

fit_plot_files <- model_data %>%
  filter(success) %>%
  mutate(safe_filename = str_replace_all(pet, "[^A-Za-z0-9_-]", "_")) %>%
  {future_pmap(
    list(.$fit_nestedsrtm, .$pet, .$safe_filename),
    function(fit, pet, fname) {
      pages <- plot(fit)
      if (inherits(pages, "ggplot")) pages <- list(pages)
      imap_chr(pages, function(p, i) {
        p <- p +
          labs(subtitle = pet, y = "Radioactivity (kBq)", x = "Time (min)") +
          theme_light()
        filepath <- file.path(fit_plot_dir,
                              paste0("fit_", fname, "_page", i, ".png"))
        ggsave(filepath, p, width = 9, height = 4, dpi = 96)
        filepath
      })
    }, .options = furrr_options(seed = TRUE))} %>%
  flatten_chr()

if (embed_fit_plots) {
  walk(fit_plot_files, ~cat("![](", .x, ")\n\n", sep = ""))
} else {
  cat(str_glue("\n\n**Note:** fit plots for {n_fit_meas} measurements saved to: `reports/{desc}_report_plots/fit/`\n\n"))
}
```

### Residuals

```{r, results='asis'}
n_res_meas <- nrow(model_data %>% filter(success))
embed_res_plots <- n_res_meas <= 50

if (embed_res_plots) {
  res_plot_dir <- tempdir()
} else {
  res_plot_dir <- file.path(analysis_folder, "reports",
                        paste0(desc, "_report_plots"), "residuals")
  dir.create(res_plot_dir, recursive = TRUE, showWarnings = FALSE)
}

res_plot_files <- model_data %>%
  filter(success) %>%
  mutate(safe_filename = str_replace_all(pet, "[^A-Za-z0-9_-]", "_")) %>%
  {future_pmap_chr(
    list(.$fit_nestedsrtm, .$pet, .$safe_filename),
    function(fit, pet, fname) {
      resid_data <- fit$tacs %>%
        mutate(Residuals = Radioactivity - Fitted)
      p <- ggplot(resid_data, aes(x = Time, y = Residuals)) +
        geom_point(aes(size = Weights)) +
        geom_line(alpha = 0.5) +
        geom_hline(yintercept = 0, linetype = "dashed") +
        facet_wrap(~Region) +
        scale_size(range = c(1, 3)) +
        guides(size = "none") +
        labs(title = pet, x = "Time (min)", y = "Residuals") +
        theme_light()
      filepath <- file.path(res_plot_dir, paste0("res_", fname, ".png"))
      ggsave(filepath, p, width = 9, height = 6, dpi = 96)
      filepath
    }, .options = furrr_options(seed = TRUE))}

if (embed_res_plots) {
  walk(res_plot_files, ~cat("![](", .x, ")\n\n", sep = ""))
} else {
  cat(str_glue("\n\n**Note:** residual plots for {n_res_meas} measurements saved to: `reports/{desc}_report_plots/residuals/`\n\n"))
}
```




# Saving Parameters

## Main TSV

```{r}
savepar <- inner_join(par_table,
                      par_se_table) %>%
  inner_join(gof_table) %>%
  # Fixing parameter names
  rename_with(~str_replace(.x, "\\.se", "-se"))

write_tsv(savepar,
          file=paste0(analysis_folder, "/",
                      "model-", "nestedSRTM","_",
                      "desc-", desc,"_",
                      "kinpar.tsv"))
```

## PET Folder TSVs

```{r}
folder_data <- tibble(
  filename = tacs_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  mutate(dirname = dirname(filename)) %>%
  select(-filename, -basename, -measurement, -desc)

savepar_pet <- savepar %>%
    group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet")))) %>%
  nest(.key="kinpars") %>%
  inner_join(folder_data) %>%
  mutate(filename = paste0(analysis_folder, "/", dirname, "/", pet, "_",
                           "model-", "nestedSRTM","_",
                            "desc-", desc,"_",
                            "kinpar.tsv"))

walk2(savepar_pet$kinpars, savepar_pet$filename, ~write_tsv(.x, .y))
```

```{r}
savepar_pet <- savepar_pet %>%
  group_by(pet) %>%
  mutate(jsondat = map(kinpars, ~list(
      Description = paste("Nested Simplified Reference Tissue Model fit using nonlinear",
                          "least squares estimation, with k2prime shared across regions",
                          "within each measurement."),
      ModelName = "nestedSRTM",
      AdditionalModelDetails = str_glue("Reference tissue model - no blood data required. Region weighting: {config_items$`Region Weighting`}.")))) %>%
  mutate(jsondat = jsonlite::toJSON(jsondat, pretty = TRUE, auto_unbox = TRUE)) %>%
  mutate(filename_json = str_replace(filename, ".tsv", ".json"))

walk2(savepar_pet$jsondat,
      savepar_pet$filename_json,
      ~writeLines(.x, .y))
```

# Saving Fitted Values

## PET Folder TSVs

```{r}
savefits <- model_data %>%
  filter(success) %>%
  mutate(fitvals = map(fit_nestedsrtm, ~{
    .x$tacs %>%
      select(
        region = Region,
        frame_mid = Time,
        Reference,
        TAC = Radioactivity,
        TAC_fitted = Fitted,
        weights = Weights
      ) %>%
      arrange(region, frame_mid)
  })) %>%
  select(any_of(c("sub", "ses", "task", "trc", "run",
                  "rec")), pet, fitvals) %>%
  unnest(cols=c("fitvals")) %>%
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet")))) %>%
  nest(.key="fitvals")

savefits_pet <- savefits %>%
  inner_join(folder_data) %>%
  mutate(filename = paste0(analysis_folder, "/", dirname, "/", pet, "_",
                           "model-", "nestedSRTM","_",
                            "desc-", desc,"fitted",
                            "_",
                            "tacs.tsv"))

walk2(savefits_pet$fitvals, savefits_pet$filename, ~write_tsv(.x, .y))
```

```{r}
savefits_pet <- savefits_pet %>%
  group_by(pet) %>%
  mutate(jsondat = map(fitvals, ~list(
      Description = "Nested Simplified Reference Tissue Model fitted values.",
      ModelName = "nestedSRTM",
      frame_mid = "The frame middle time in minutes",
      TAC = "TAC radioactivity data in kBq to which the model was fitted.",
      TAC_fitted = "Model fitted values.",
      weights = "Model weights"))) %>%
  mutate(jsondat = jsonlite::toJSON(jsondat, pretty = TRUE, auto_unbox = TRUE)) %>%
  mutate(filename_json = str_replace(filename, ".tsv", ".json"))

walk2(savefits_pet$jsondat,
      savefits_pet$filename_json,
      ~writeLines(.x, .y))
```




```{r cleanup, include=FALSE}
future::plan(future::sequential)
```

# Session Information

```{r session-info}
sessionInfo()
```
