---
title: "SUV / SUVR Estimation Report"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
params:
  cores: 1
  model_number: "Model 1"
  analysis_folder: NULL
  bids_dir: NULL
  blood_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = FALSE)
# Warnings go to the console/step log, not into this report: dplyr's
# many-to-many join warning is the signal that a duplicated record has
# multiplied TAC rows, and it used to be discarded outright.
petfit::divert_report_warnings()
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(kinfitr)
library(knitr)
library(jsonlite)
library(glue)
library(DT)
library(furrr)

# Fixed seed for consistency with the fitting reports. SUVR itself is
# deterministic, but furrr_options(seed = TRUE) still derives its streams from
# the session state, so seeding here keeps a re-run byte-identical.
set.seed(123)

cores <- params$cores %||% 1
if (cores > 1) {
  if (future::supportsMulticore()) {
    future::plan(future::multicore, workers = cores)
  } else {
    future::plan(future::multisession, workers = cores)
  }
} else {
  future::plan(future::sequential)
}

theme_set(theme_light())

analysis_folder <- params$analysis_folder
# The units of the TACs everything downstream is derived from, recorded by
# the region definition step. Read rather than assumed, so that the sidecars
# written below cannot claim units the data does not have.
tac_units <- petfit_tac_units(analysis_folder)
model_number <- params$model_number
bids_dir <- params$bids_dir

config_path <- file.path(analysis_folder, "desc-petfitoptions_config.json")
config <- NULL
if (file.exists(config_path)) {
  tryCatch({
    config <- jsonlite::fromJSON(config_path)
    config <- coerce_bounds_numeric(config)
  }, error = function(e) {
    cat("Warning: Could not load config file:", e$message, "\n")
  })
} else {
  cat("Config file not found at:", config_path, "\n")
}
```

```{r cleanup-old, include=FALSE}
desc <- str_remove(str_to_lower(model_number), " ")
oldfiles <- list.files(analysis_folder, pattern = desc,
                       recursive = TRUE, full.names = TRUE)
file.remove(oldfiles)
```

This report summarises the estimation step using the Standardised Uptake Value (SUV) and the Standardised Uptake Value Ratio (SUVR): each region's integral over a frame or time window, and the target-to-reference ratio of those integrals.

SUVR is a ratio of two integrals over the same frames, so the injected radioactivity and body weight cancel and it is always available. SUV does not cancel, and is only reported when the injected radioactivity is known for every measurement. A time window includes whole frames whose midpoint falls inside it, and the window which was integrated is reported alongside every estimate.

# Analysis Configuration

**Model:** `r params$model_number` - SUV / SUVR (AUC ratio)

**Analysis folder:** `r params$analysis_folder`

**Generated on:** `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`

# Model Configuration

```{r model-config}
model_config <- NULL
if (!is.null(config$Models)) {
  if (params$model_number == "Model 1") {
    model_config <- config$Models$Model1
  } else if (params$model_number == "Model 2") {
    model_config <- config$Models$Model2
  } else if (params$model_number == "Model 3") {
    model_config <- config$Models$Model3
  }
}

if (!is.null(model_config) && model_config$type == "SUVR") {
  config_items <- list("Model Type" = "SUV / SUVR")

  subset_type <- model_config$subset$type %||% "none"

  if (!is.null(model_config$subset) && subset_type %in% c("frame", "time")) {
    subset_info <- paste0(
      "Type: ", subset_type,
      ", Start: ", model_config$subset$start %||% "Not set",
      ", End: ", model_config$subset$end %||% "Not set"
    )
    config_items[["Window"]] <- subset_info
  } else {
    config_items[["Window"]] <- "Use all frames"
  }

  config_df <- tibble(
    Parameter = names(config_items),
    Value = map_chr(config_items, as.character)
  )

  kable(config_df, caption = "SUV / SUVR Configuration")
} else {
  cat("SUVR configuration not found or incomplete.")
}
```

```{r setup-conditions, echo=FALSE}
has_suvr_config <- !is.null(model_config) && model_config$type == "SUVR"

if (!has_suvr_config) {
  cat("Invalid or missing SUVR configuration. This report should not have been generated.")
  knitr::knit_exit()
}
```

# Loading Data

## Loading TAC Data

```{r load-tacs}
tacs_files <- list.files(analysis_folder,
                         pattern = "*_desc-targetregions_tacs.tsv",
                         recursive = TRUE)

if (length(tacs_files) == 0) {
  stop("No target TAC files found in analysis folder: ", analysis_folder)
}

tac_data <- tibble(filename = tacs_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>%
  unnest(tacs) %>%
  select(-basename, -measurement, -desc)
```

## Loading Reference TAC Data

```{r load-reftac}
ref_files <- list.files(analysis_folder,
                        pattern = "*_desc-ref_tacs.tsv",
                        recursive = TRUE)

if (length(ref_files) == 0) {
  stop("No reference TAC files found in analysis folder: ", analysis_folder)
}

ref_data <- tibble(filename = ref_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(ref_tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>%
  unnest(ref_tacs) %>%
  select(-basename, -measurement, -desc, -filename) %>%
  select(-any_of("volume_mm3"))
```

# Combining Data

```{r combine-data}
model_data <- tac_data %>%
  inner_join(ref_data) %>%
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet", "filename", "region",
                                           "InjectedRadioactivity", "bodyweight")))) %>%
  mutate(frame_start = frame_start / 60,
         frame_end = frame_end / 60,
         frame_dur = frame_dur / 60,
         frame_mid = frame_mid / 60) %>%
  arrange(frame_start, .by_group = TRUE) %>%
  nest(.key = "tacs") %>%
  ungroup() %>%
  mutate(output_stem = filename) %>%
  select(-filename) %>%
  mutate(output_stem = str_remove(output_stem, "_desc.*")) %>%
  mutate(output_stem = str_remove(output_stem, "_tacs.*"))
```

# SUV / SUVR Estimation

## SUV Availability

```{r suv-availability, results='asis'}
# Decide how SUV should be calculated.
inj_rad_col <- if ("InjectedRadioactivity" %in% colnames(model_data)) {
  model_data$InjectedRadioactivity
} else NULL
bodyweight_col <- if ("bodyweight" %in% colnames(model_data)) {
  model_data$bodyweight
} else NULL

suv_info <- suv_denominator(inj_rad_col, bodyweight_col)

# An assumed body weight changes what the SUV column means for every row, so it
# is stated as a warning rather than a note.
if (suv_info$mode == "SUV_bw70") {
  str_glue("> **Warning: {suv_info$label}** The assumed weight is applied to ",
           "every measurement, including those whose body weight is known, so ",
           "that SUV means the same thing across the cohort. SUV is therefore ",
           "approximate, and not comparable with SUV calculated from measured ",
           "body weights. SUVR is unaffected: it is a ratio, so the ",
           "denominator cancels.")
} else {
  str_glue("{suv_info$label}")
}
```

```{r suv-denominator}
# Per-measurement dose and body mass to hand to suvr(). A denominator of 1 is
# kinfitr's convention for "no dose": the SUV outcomes then come back in units
# of radioactivity concentration, recorded as SUV_denominator, and are dropped
# from the results below. The SUVR is a ratio, so it is unaffected either way.
if (suv_info$mode == "none") {
  model_data$injRad_used <- 1
  model_data$bodymass_used <- 1
} else {
  model_data$injRad_used <- model_data$InjectedRadioactivity
  # suv_denominator() returns the body mass in grams, whether it is the measured
  # weight or the assumed 70 kg, so that the SUV comes out in the conventional
  # g/mL rather than kg/mL.
  model_data$bodymass_used <- suv_info$bodymass
}
```

## Estimation

```{r window-config}
# Resolve the configured window. suvr() normalises a one-sided window and
# resolves a time window to whole frames, so nothing more is needed here.
subset_config <- model_config$subset

frameStartEnd <- NULL
timeStartEnd <- NULL

if (!is.null(subset_config) && (!is.null(subset_config$start) || !is.null(subset_config$end))) {
  if (identical(subset_config$type, "frame")) {
    frameStartEnd <- c(subset_config$start, subset_config$end)
  } else if (identical(subset_config$type, "time")) {
    timeStartEnd <- c(subset_config$start, subset_config$end)
  }
}
```

```{r suvr-estimation, report_warnings=TRUE}
safe_suvr <- safely(kinfitr::suvr)

model_data <- model_data %>%
  mutate(suvr_attempt = future_pmap(
    list(tacs, injRad_used, bodymass_used),
    ~safe_suvr(t_tac  = ..1$frame_mid,
               reftac = ..1$RefTAC,
               roitac = ..1$TAC,
               dur    = ..1$frame_dur,
               injRad   = ..2,
               bodymass = ..3,
               frameStartEnd = frameStartEnd,
               timeStartEnd  = timeStartEnd),
    .options = furrr_options(seed = TRUE)
  )) %>%
  mutate(suvr_fit = map(suvr_attempt, "result"),
         suvr_error = map_chr(suvr_attempt,
                              ~if (is.null(.x$error)) NA_character_ else conditionMessage(.x$error))) %>%
  select(-suvr_attempt) %>%
  mutate(success = map_lgl(suvr_fit, ~!is.null(.x) && !is.null(.x$par) &&
                                       nrow(.x$par) == 1 && is.finite(.x$par$SUVR)),
         par = map(suvr_fit, ~if (!is.null(.x)) .x$par else NULL),
         fitvals = map(suvr_fit, ~if (!is.null(.x)) .x$tacs else NULL))

# suvr() can return without raising a condition and still give a SUVR which is
# not a number: the ratio is undefined when the reference region integrates to
# zero over the window, and infinite when it is negligible beside the target.
# Such a measurement is unsuccessful, so it needs a reason of its own or it is
# counted below without ever being explained.
model_data <- model_data %>%
  mutate(suvr_error = map2_chr(suvr_fit, suvr_error, ~{
    # An error was already raised, or nothing came back at all: that reason
    # stands.
    if (!is.na(.y) || is.null(.x)) return(.y)

    suvr <- if (is.null(.x$par) || nrow(.x$par) != 1) NA_real_ else .x$par$SUVR
    if (is.finite(suvr)) return(NA_character_)

    if (is.na(suvr)) {
      paste("SUVR is not a number: both the target and the reference region",
            "integrate to zero over the window, so the ratio is undefined.")
    } else {
      paste("SUVR is infinite: the reference region integrates to zero over",
            "the window.")
    }
  }))
```

```{r estimation-summary, results='asis'}
success_n <- sum(model_data$success)
tot_n <- nrow(model_data)

str_glue("SUVR successfully estimated for {success_n} / {tot_n} ({round(100 * success_n / tot_n)}%) of region-measurements.

         SUVR estimation unsuccessful for {tot_n - success_n} / {tot_n} ({100 - round(100 * success_n / tot_n)}%) of region-measurements.")
```

```{r estimation-errors, results='asis'}
# Say why, rather than only how many.
estimation_errors <- model_data %>%
  filter(!is.na(suvr_error)) %>%
  count(suvr_error, name = "n_region_measurements")

if (nrow(estimation_errors) > 0) {
  print(kable(estimation_errors, caption = "Reasons for unsuccessful estimation"))
}
```

# Results

```{r}
model_data <- model_data %>%
  filter(success)

if (nrow(model_data) == 0) {
  stop("SUVR could not be estimated for any region-measurement.")
}
```

## Parameters

### Estimates

```{r results-table}
model_data <- model_data %>%
  mutate(
    window_start = map2_dbl(tacs, suvr_fit, ~min(.x$frame_start[.y$tacs$Included])),
    window_end   = map2_dbl(tacs, suvr_fit, ~max(.x$frame_end[.y$tacs$Included]))
  )

par_table <- model_data %>%
  ungroup() %>%
  select(-tacs, -suvr_fit, -fitvals, -output_stem,
         -any_of(c("injRad_used", "bodymass_used", "success", "suvr_error"))) %>%
  unnest(par) %>%
  relocate(window_start, window_end, .before = window_duration)

# Drop the SUV columns entirely when there is no dose information, rather than
# showing a column of NAs.
if (suv_info$mode == "none") {
  par_table <- par_table %>%
    select(-any_of(c("SUV", "SUV_ref", "SUV_AUC", "SUV_ref_AUC", "SUV_denominator")))
}

par_table %>%
  select(where(~ n_distinct(.x) > 1)) %>%
  mutate(across(where(is.numeric), ~round(.x, 3))) %>%
  DT::datatable()
```

### Parameter Plots

```{r hist-data}
hist_pars <- intersect(c("SUVR", "SUV", "SUV_ref", "SUV_denominator"),
                       colnames(par_table))

par_table_long <- par_table %>%
  select(region, all_of(hist_pars)) %>%
  pivot_longer(cols = all_of(hist_pars),
               names_to = "Parameter",
               values_to = "Value") %>%
  mutate(Parameter = factor(Parameter, levels = hist_pars))
```

#### Overall Histogram

```{r, fig.width=7, fig.height=7}
ggplot(par_table_long, aes(x=Value, fill=Parameter)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free", ncol=2) +
  guides(fill="none")
```

#### Histograms By Region

```{r, fig.width=7, fig.height=7}
ggplot(par_table_long, aes(x=Value, fill=region)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free", ncol=2)
```

## Integration Windows

### Plots

The shaded frames are those which were integrated: the ratio of the two shaded areas is the SUVR.

```{r, results='asis'}
n_fit_plots <- nrow(model_data)
embed_fit_plots <- n_fit_plots <= 200

if (embed_fit_plots) {
  fit_plot_dir <- tempdir()
} else {
  fit_plot_dir <- file.path(analysis_folder, "reports",
                        paste0(desc, "_report_plots"), "fit")
  dir.create(fit_plot_dir, recursive = TRUE, showWarnings = FALSE)
}

refname <- config$ReferenceTAC$region %||% "Reference"

fit_plot_files <- model_data %>%
  mutate(SUVR = map_dbl(par, "SUVR"),
         n_frames = map_dbl(par, "n_frames"),
         title = paste(pet, " : ", region),
         subtitle = str_glue("SUVR = {signif(SUVR, 4)} | window ",
                             "{signif(window_start, 4)}-{signif(window_end, 4)} min ",
                             "({n_frames} frames)"),
         safe_filename = str_replace_all(
           paste(pet, region, sep = "_"), "[^A-Za-z0-9_-]", "_")) %>%
  {future_pmap_chr(
    list(.$suvr_fit, .$region, .$title, .$subtitle, .$safe_filename),
    function(fit, region, title, subtitle, fname) {
      p <- kinfitr::plot_suvrfit(fit, roiname = region, refname = refname) +
        labs(title = title, #subtitle = subtitle,
             y = "Radioactivity (kBq)", x = "Time (min)") +
        theme_light()
      filepath <- file.path(fit_plot_dir, paste0("fit_", fname, ".png"))
      ggsave(filepath, p, width = 6, height = 4, dpi = 96)
      filepath
    }, .options = furrr_options(seed = TRUE))}

if (embed_fit_plots) {
  walk(fit_plot_files, ~cat("![](", .x, ")\n\n", sep = ""))
} else {
  cat(str_glue("\n\n**Note:** {n_fit_plots} window plots saved to: `reports/{desc}_report_plots/fit/`\n\n"))
}
```

# Saving Parameters

## Main TSV

```{r save-main-parameters}
savepar <- par_table

write_tsv(savepar,
          file = paste0(analysis_folder, "/",
                        "model-", "SUVR", "_",
                        "desc-", desc, "_",
                        "kinpar.tsv"))
```

## PET Folder TSVs

```{r save-pet-parameters}
folder_data <- tibble(filename = tacs_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  mutate(dirname = dirname(filename)) %>%
  select(-filename, -basename, -measurement, -desc)

savepar_pet <- savepar %>%
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet")))) %>%
  nest(.key = "kinpars") %>%
  inner_join(folder_data) %>%
  mutate(filename = paste0(analysis_folder, "/", dirname, "/", pet, "_",
                           "model-", "SUVR", "_",
                           "desc-", desc, "_",
                           "kinpar.tsv"))

walk2(savepar_pet$kinpars, savepar_pet$filename, ~write_tsv(.x, .y))
```

```{r save-parameter-json}
savepar_pet <- savepar_pet %>%
  group_by(pet) %>%
  mutate(jsondat = map(kinpars, ~c(list(
    Description = "Standardised Uptake Value (SUV) and Uptake Value Ratio (SUVR), estimated as target and reference tissue AUCs over a frame or time window, and their ratio.",
    ModelName = "SUVR",
    AdditionalModelDetails = "Reference tissue ratio - no blood data required",
    SUVCalculation = suv_info$label,
    WindowConvention = "A time window includes whole frames whose midpoint falls within it. The window actually integrated is recorded per row."),
    bids_column_units(c(list(
      SUVR = "Target region AUC divided by reference region AUC over the window. Dose and body weight cancel, so this is unaffected by whether SUV could be calculated. Dimensionless.",
      window_start = "Window start time",
      window_end = "Window end time",
      window_duration = "Total included frame duration",
      n_frames = "Number of frames included in the ratio"
    ), if (suv_info$mode == "none") list() else list(
      SUV = "Mean target SUV over the window",
      SUV_ref = "Mean reference SUV over the window",
      SUV_AUC = "Target region SUV integral over the window",
      SUV_ref_AUC = "Reference region SUV integral over the window",
      SUV_denominator = "Injected radioactivity divided by body mass, as applied to the SUV outcomes"
    )),
    radioactivity_units = tac_units$radioactivity,
    time_units = "min")))) %>%
  mutate(jsondat = map_chr(jsondat, ~jsonlite::toJSON(.x, pretty = TRUE, auto_unbox = TRUE))) %>%
  mutate(filename_json = str_replace(filename, ".tsv", ".json"))

walk2(savepar_pet$jsondat,
      savepar_pet$filename_json,
      ~writeLines(.x, .y))
```

# Saving Integration Inputs

## PET Folder TSVs

```{r save-fitvals}
savefits <- model_data %>%
  select(any_of(c("sub", "ses", "task", "trc", "run",
                  "rec", "pet", "region")), fitvals) %>%
  unnest(cols = c("fitvals")) %>%
  select(any_of(c("sub", "ses", "task", "trc", "run", "rec", "pet", "region",
                  "Time", "Duration", "Target", "Reference", "Included"))) %>%
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task",
                                           "run", "pet")))) %>%
  nest(.key = "fitvals")

savefits_pet <- savefits %>%
  inner_join(folder_data) %>%
  mutate(filename = paste0(analysis_folder, "/", dirname, "/", pet, "_",
                           "model-", "SUVR", "_",
                           "desc-", desc, "ratioinput",
                           "_",
                           "tacs.tsv"))

walk2(savefits_pet$fitvals, savefits_pet$filename, ~write_tsv(.x, .y))
```

```{r save-fitvals-json}
savefits_pet <- savefits_pet %>%
  group_by(pet) %>%
  mutate(jsondat = map(fitvals, ~c(list(
      Description = "TAC values used for SUV / SUVR estimation.",
      ModelName = "SUVR"),
      bids_column_units(list(
        Time = "Frame midpoint time",
        Duration = "Frame duration",
        Target = "Target region TAC radioactivity data",
        Reference = "Reference region TAC radioactivity data",
        Included = "Whether the frame contributed to the window"),
        radioactivity_units = tac_units$radioactivity,
        time_units = "min")))) %>%
  mutate(jsondat = map_chr(jsondat, ~jsonlite::toJSON(.x, pretty = TRUE, auto_unbox = TRUE))) %>%
  mutate(filename_json = str_replace(filename, ".tsv", ".json"))

walk2(savefits_pet$jsondat,
      savefits_pet$filename_json,
      ~writeLines(.x, .y))
```

```{r cleanup, include=FALSE}
future::plan(future::sequential)
```

# Session Information

```{r session-info}
sessionInfo()
```
